---
title: "DSM Project Data Collection: Web Scrapting json using R"
author: "Chenxi Li"
date: "10/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Collect Event Attendance Info from API

In this part, we use the Meetup API instead of scrapting data directly from webpage.
The source of api is at here (https://www.meetup.com/meetup_api/).


### Sample of Attendance Data for One Event

```{r}
# r web / r json - installing jsonlite
#install.packages("jsonlite")
rm(list = ls())
library("jsonlite")

# r web / r json - get json data from url
json_file <- "https://api.meetup.com/Des-Moines-Data-Analytics/events/243781906/attendance?page=50"
data <- fromJSON(json_file, flatten = TRUE)
#head(data %>% bind_rows() %>% mutate(department = rep(names(data), map_dbl(data, nrow))))
str(as.data.frame(data))
```

```{r}
# 2021-10-08 11:31
tdat <- data$rsvp.updated[5]
datetime <- as.POSIXct(strptime(tdat, format = "%d/%m/%Y %H:%M:%S"))
datetime <- as.POSIXct(as.numeric(tdat)/1000, origin='2021-10-08') 
datetime

format(as.POSIXct("1970-01-01",tz="GMT")+tdat/1000-5*3600, "%Y-%m-%d %H:%M:%S")

t.gmt <- as.POSIXct((tdat)/1000, origin = Sys.Date(), tz = "GMT", format = "%Y-%m-%d %H:%M:%S") 
t.gmt #"2073-07-28 16:31:21 GMT"
t.local <- as.POSIXct(format(t.gmt, "%Y-%m-%d %H:%M:%S"))
t.local
```
```{r}
data$rsvp.updated <- format(as.POSIXct("1970-01-01",tz="GMT")+data$rsvp.updated/1000-5*3600, "%Y-%m-%d %H:%M:%S")
head(data)
```

## 

```{r}
json_file <- "https://api.meetup.com/Des-Moines-Data-Analytics/members/"
Members <- fromJSON(json_file, flatten = TRUE)
head(as.data.frame(Members))
```



### Loop of Scrapting

```{r}
df <- read.csv("Event.csv")
#df <- df[1:1121, ]
df$ï..EventID[41] <- 281103430
head(df)
```


```{r}
lsCol <- c("event.id", "status", "member.id","member.name", "member.bio" ,"member.role", "member.photo.id", "rsvp.response", "rsvp.updated")

data_comb <- data.frame(matrix(ncol = 9, nrow = 0))
colnames(data_comb) <- lsCol

for (curr_url in df$ï..EventID) {
  
  json_file <- paste("https://api.meetup.com/Des-Moines-Data-Analytics/events/", curr_url,"/attendance?page=100", sep="")
  data <- fromJSON(json_file, flatten = TRUE)
  data$rsvp.updated <- format(as.POSIXct("1970-01-01",tz="GMT")+data$rsvp.updated/1000-5*3600, "%Y-%m-%d %H:%M:%S")
  data$event.id <- curr_url
  if ("status" %in% colnames(data) == FALSE){
    data$status <- "missing"
    print(curr_url)
  }
  data_comb <- rbind(data_com-
                       b, data[,lsCol])
  
  print(curr_url)

```

```{r}
write.csv(data_comb, file="event_update.csv")
```


## Collect list of interest from Webpage

The interest cannot be collect via API directly, so we use the web-scraping technique.
We think that interest may also affect the event attendance, but there are too many interests. We were not able to classify them into different category and use in analysis.
We put the code here in case you are interesting for further analysis.


### Sample of Collection

```{r}
library(RCurl)
library(rvest)
library(stringr)

url <- "http://www.meetup.com/Des-Moines-Data-Analytics/members/224220146/"
page <- read_html(url)

interest <- 
  page %>% 
  html_nodes('li[class="D_group small last"]') %>%
  html_nodes('a[class="link"]') %>%
  html_text()
  
interest <- paste(interest, collapse=", ")
interest

```

### Loop of Data Collection

```{r}
df <- read.csv("Import.csv")
```

You may remove the comment if you hope to collect Intro and Comment info at the same time.
It is also possible to collect them via API, which is much easier. 

```{r}
irow = 1

#vIntro <- c()
#vComment <- c()
vInterest <- c()


for (curr_url in df$URL.of.Member.Profile) {
  tryCatch({
  print(curr_url)
  Sys.sleep(2)
  
  an.error.occured <- FALSE
  
  page <- read_html(curr_url)

  }, error=function(e){
    cat("ERROR: [", irow, "]", conditionMessage(e), "\n")
    an.error.occured <<- TRUE
    }) 
  
  #intro <- ifelse(an.error.occured, "", html_text(html_nodes(page,'p'), trim = TRUE)[3])
  #comments <- ifelse(an.error.occured, "", html_text(html_nodes(page,'p'))[4])
  interest <- ifelse(an.error.occured, "",  
      page %>% 
      html_nodes('li[class="D_group small last"]') %>%
      html_nodes('a[class="link"]') %>%
      html_text() %>%
      paste(collapse=", "))
  
  
  #df[irow, "Introduction"] <- intro
  #df[irow, "Comment"] <- comments
  df[irow, "Interests"] <- interest
  
  irow = irow + 1
}


df[5:10, c("Interests")]
```






